Democracy, Public Support, and Measurement Uncertainty

### 2021-07-20 paper/dcpo_demsupport.Rmd
var label updated

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",
    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",
    `diff(Liberal_z, lag = 1)` = "Delta~Support(electoral)",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Support(electoral)",
    `plm::lag(Liberal_z, 1)` = "Support[t-1](electoral)",
    `plm::lag(Vdem_liberal_z, 1)` = "Support[t-1](electoral)",
    `diff(Polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Support(minoritarian)",
    `plm::lag(Polyarchy_z, 1)` = "Support[t-1](minoritarian)",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Support[t-1](minoritarian)",
    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
    # `Corrup_TI_z` = "Log~Corruption[t-1]"
)
```

>>>>

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",

    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",

    `diff(Liberal_z, lag = 1)` = "Delta~Electoral~democracy",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Electoral~democracy",
    `plm::lag(Liberal_z, 1)` = "Electoral~democracy[t-1]",
    `plm::lag(Vdem_liberal_z, 1)` = "Electoral~democracy[t-1]",

    `diff(Polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
    `plm::lag(Polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",

    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
    # `Corrup_TI_z` = "Log~Corruption[t-1]"
)
```
